A Java Wrapper For Embarresingly Parallel Problems

### 2013-10-10 paper/paper.tex
More papaer

\documentclass[12pt]{article} 
\usepackage{graphics}
\usepackage{setspace}

@@

Instead of attempting to rewrite the preexisting program, blah. Trying to
parallelize the serial KaKs Calculator program would have presented several
problems: introducing bugs, breaking the KaKs algorithm, and the learning curve
of C++ threading. With such a short time before results were needed, a different
approach was necessary. A simple Java program was written to break up the input
and spawn threads that would run BLANKS's KaKs Calculator. When the input was
calculated, the contents of the output files was concatenated together to
produce a final input. MORE?

The KaKs Calculator is not the only embarresingly parallel program that has the
potential to take several days to run on a data set. In fact, there are several
embarresingly parallel programs in the biological sciences. TALK ABOUT OTHER
PROGRAMS HERE. With this multitude of applications that would benefit from
parallelism, it was obvious that the wrapper program has potential outside of
this project.

TALK ABOUT PAPER HERE. AND MAYBE THE POWERPOINT TOO.

@@

The KaKs Calculator is not the only program to used the wrapper; there are
various potential programs that the wrapper could support. SENTANCE. The wrapper
needs to support various kinds of input files and be able to chunk up the work
accordingly. The KaKs Calculator's input consists of a header and then two
protein sequence lines followed by a blank line. The wrapper will use that blank
line to know when one chunk of work has ended and another has begun. The user
can input their own regular expression to determine what lines of input make up
what chunks. This will occur in the ChunkManager class.

The other purpose of the ChunkManager class is to combine the resulting chunks 
back together when the worker threads have finished. MORE

>>>>

\documentclass[12pt]{article} 
\usepackage{graphics}
\usepackage{setspace}
\usepackage{cite}

@@

Instead of attempting to rewrite the preexisting program, we decided it would be
better to look at other options. Trying to parallelize the serial KaKs 
Calculator program could present several problems: introducing bugs, breaking 
the KaKs algorithm, and the learning curve of C++ threading. We decided a 
different approach was neccessary, mostly due to the short time table to produce
results. A simple Java program was written to break up the input and spawn 
threads that would run BLANKS's KaKs Calculator\cite{blah}. When the input was 
calculated, the contents of the output files was concatenated together 
to produce a final input.

The KaKs Calculator is not the only embarresingly parallel program that has the
potential to take several days to run on a data set. In fact, there are several
embarresingly parallel programs in the biological sciences. TALK ABOUT OTHER

BLAST, two other things are

PROGRAMS HERE. With this multitude of applications that would benefit from
parallelism, it was obvious that the wrapper program has potential outside of
this project.

% TALK ABOUT PAPER HERE. AND MAYBE THE POWERPOINT TOO.

@@

The KaKs Calculator is not the only program to use the wrapper; there are
various potential programs that the wrapper could support. The only requirements
for the this program are that it process the input in an embarresingly parallel
manner and that the input comes from a file and the processed results are also
writen to a file. The wrapper needs to support various kinds of input files and 
be able to chunk up the work accordingly. The KaKs Calculator's input consists 
of a header and then two protein sequence lines followed by a blank line. The 
wrapper will use that blank line to know when one chunk of work has ended and 
another has begun. The user can input their own regular expression to determine 
what lines of input make up what chunks. This will occur in the ChunkManager 
class.

The other purpose of the ChunkManager class is to combine the resulting chunks 
back together when the worker threads have finished. Once the work has been
down, all of the seperate results are spread across several files. The
ChunkManager's second job is to retrieve those results and construct a real
output file. The real output file must look the same as the output file would
look if the program were run serially; the output must come in the same order as
the inputs in the input file and headers must be added to the top, if
applicable.
